---
title: "15-279"
author: "Alex Cookson"
date: "17/05/2020"
output: html_document
---

### Question 1

What's the difference between `if` and `ifelse()`? Carefullyy read the help and construct three examples that illustrate the key differences.


### Question 2

Write a greeting function that says "good morning," "good afternoon," or "good evening," depending on the time of day. (Hint: use a time argument that defaults to `lubridate::now()`. That will make it easier to test your function.)


### Question 3

Implement a `fizzbuzz` function. It takes a single number as input. If the number is divisible by three, it returns "fizz". If it's divisible by five, it returns "buzz". If it's divisible by three and five, it returns "fizzbuzz". Otherwise, it returns the number. Make sure you first write working code before you create the function.


### Question 4

How could you use `cut()` to simplify this set of nested if-else statements?

```{r q4, eval = FALSE}
If (temp <= 0) {
  "freezing"
} else if (temp <= 10) {
  "cold"
} else if (temp <= 20) {
  "cool"
} else if (temp <= 30) {
  "warm"
} else {
  "hot"
}
```


### Question 5

What happens if you use `switch()` with numeric values?


### Question 6

What does this `switch()` call do? What happens if x is "e"?

```{r q6, eval = FALSE}
switch(x,
  a = ,
  b = "ab",
  c = ,
  d = "cd"
)
```

Experiment, then carefully read the documentation.
