---
title: "07-123"
author: "Alex Cookson"
date: "16/05/2020"
output: html_document
---

### Question 1

How can you tell if an object is a tibble? (Hint: try printing `mtcars`, which is a regular data frame.)


### Question 2

Compare and contrast the following operations on a `data.frame` and equivalent tibble. What is different? Why might the default data frame behaviours cause you frustration?

```{r q2, eval = FALSE}
df <- data.frame(abc = 1, xyz = "a")
df$x
df[, "xyz"]
df[, c("abc", "xyz")]
```


### Question 3

If you have the name of a variable stored in an object, e.g., `var <- "mpg"`, how can you extract the reference variable from a tibble?


### Question 4

Practice referring to nonsyntactic nmes in the following data frame by:

a. Extracting the variable called `1`.
b. Plotting a scatterplot of `1` versus `2`.
c. Creating a new column called `3`, which is `2` divided by `1`.
d. Renaming the columns to `one`, `two`, and `three`:

```{r q4, eval = FALSE}
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)
```


### Question 5

What does `tibble:enframe()` do? When might you use it?


### Question 6

What option controls how many additional column names are printed at the footer of a tibble?
