---
title: "09-156"
author: "Alex Cookson"
date: "16/05/2020"
output: html_document
---

### Question 1

Why are `gather()` and `spread()` not perfectly symmetrical? Carefully consider the following example:

```{r q1, eval = FALSE}
stocks <- tibble(
  year = c( 2015,  2015, 2016, 2016),
  half = c(     1,    2,    1,    2),
  return = c(1.88, 0.59, 0.92, 0.17)
)
stocks %>%
  spread(year, return) %>%
  gather("year", "return", `2015`:`2016`)
```

(Hint: look at the variable types and think about column *names*.)

Both `spread()` and `gather()` have a `convert` argument. What does it do?


### Question 2

Why does this code fail?

```{r q2, eval = FALSE}
table4a %>%
  gather(1999, 2000, key = "year", values = "cases")
```


### Question 3

Why does spreading this tibble fail? How could you add a new column to fix the problem?

```{r q3, eval = FALSE}
people <- tribble(
  ~name,              ~key, ~value,
  #------------------/-----/------
  "Phillip Woods",   "age",     45,
  "Phillip Woods",   "height", 186,
  "Phillip Woods",   "age",     50,
  "Jessica Cordero", "age",     37,
  "Jessica Cordero", "height", 156
)
```


### Question 4

Tidy this simple tibble. Do you need to spread or gather it? What are the variables?

```{r q4, eval = FALSE}
preg <- tribble(
  ~pregnant, ~male, ~female,
  "yes",     NA,    10,
  "no",      20,    12"
)
```

