---
title: "01-012"
author: "Alex Cookson"
date: "15/05/2020"
output: html_document
---

### Question 1

What's gone wrong with this code? Why are the points not blue?

```{r q1, eval = FALSE}
ggplot(data = mpg) +
  geom_point(
    mapping = aes(x = displ, y = hwy, colour = "blue")
  )
```

-----------------------------

First, we should deduce what we are trying to do with this code: create a scatterplot of `displ` vs. `hwy`, with points manually set to "blue".

The points are blue, though, because `colour = "blue"` is *inside* the `aes()` call. Being inside `aes()` sets the colour aesthetic to a *character* value of "blue", which applies to all data. **ggplot** doesn't interpret this as setting a colour, so it uses the default red colour.

The correct code would set `colour = "blue"` *outside* the `aes()`, which we need to do when manually specifying an aesthetic:

```{r q1-answer}
ggplot(data = mpg) +
  geom_point(
    mapping = aes(x = displ, y = hwy),
    colour = "blue"
  )
```



### Question 2

Which variables in `mpg` are categorical? Which variables are continuous? (Hint: type `?mpg` to read the documentation for the dataset.) How can you see this information when you run `mpg`?

-----------------------------

Reading the documentation by running `?mpg` gives us enough information to determine which variables are categorical and continuous:

```{r q2-answer-1}
?mpg
```

- `manufacturer`: categorical
- `model`: categorical
- `displ`: continuous
- `year`: continuous
- `cyl`: continuous
- `trans`: categorical
- `drv`: categorical
- `cty`: continuous
- `hwy`: continuous
- `fl`: categorical
- `class`: categorical

We could also run `mpg` and look at the class of the variable -- character, double, integer, etc. Between the class of the variable and the first 10 observations displayed, you should be able to figure out which variables are categorical or continuous

```{r q2-answer-2}
mpg
```



### Question 3

Map a continuous variable to `colour`, `size`, and `shape`. How do these aesthetics behave differently for categorical versus continuous variables?

-----------------------------

Let's create a scatterplot of `hwy` vs. `cty` mileage, with `cyl`, numbers of cylinders, mapped to the aesthetics in the question.

```{r q3-answer-1}
# colour
ggplot(data = mpg) +
  geom_point(
    mapping = aes(x = hwy, y = cty, colour = cyl)
  )
```

When mapped to `colour`, `cyl` values are on a gradient, with high values as light blue and low values as dark blue.

```{r q3-answer-2}
# size
ggplot(data = mpg) +
  geom_point(
    mapping = aes(x = hwy, y = cty, size = cyl)
  )
```

When mapped to `size`, high `cyl` values have large points and low `cyl` values have small points.

```{r q3-answer-3}
# shape
ggplot(data = mpg) +
  geom_point(
    mapping = aes(x = hwy, y = cty, shape = cyl)
  )
```

When mapped to `shape`, we get an error message and nothing is graphed. Shapes don't have a natural ordering to them in the same way `colour` and `size` do, so **ggplot** doesn't know what to do with it.



### Question 4

What happens if you map the same variable to multiple aesthetics?


### Question 5

What does the `stroke` aesthetic do? What shapes does it work with? (Hint: use `?geom_point`.)


### Question 6

What happens if you map an aesthetic to something other than a variable name, like `aes(colour = displ < 5)`?

