---
title: "01-020"
author: "Alex Cookson"
date: "15/05/2020"
output: html_document
---

### Question 1

What geom would you use to draw a line chart? A boxplot? A histogram? An area chart?


### Question 2

Run this code in your head and predict what the output will look like. Then, run the code in R and check your predictions:

```{r q2, eval = FALSE}
ggplot(
  data = mpg,
  mapping = aes(x = displ, y = hwy, colour = drv)
) +
  geom_point() +
  geom_smooth(se = FALSE)
```


### Question 3

What does `show.legend = FALSE` do? What happens if you remove it? Why do you think I used it earlier in the chapter?


### Question 4

What does the `se` argument to `geom_smooth()` do?


### Question 5

Will these two graphs look different? Why/why not?

```{r q5, eval = FALSE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point() +
  geom_smooth()

ggplot() +
  geom_point(
    data = mpg,
    mapping = aes(x = displ, y = hwy)
  ) +
  geom_smooth(
    data = mpg,
    mapping = aes(x = displ, y = hwy)
  )
```


### Question 6

Recreate the R code necessary to generate the following graphs. (Consult page 21 for graphs.)

