---
title: "01-015"
author: "Alex Cookson"
date: "15/05/2020"
output: html_document
---

### Question 1

What happens if you facet on a continuous variable?


### Question 2

What do the empty cells in a plot with `facet_grid(drv ~ cyl)` mean? How do they relate to this plot?

```{r q2, eval = FALSE}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = drv, y = cyl))
```


### Question 3

What plots does the following code make? What does `.` do?

```{r q3}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)

ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```


### Question 4

Take the first faceted plot in this section:

```{r q4, eval = FALSE}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_wrap(~ class, nrow = 2)
```

What are the advantages to using faceting instead of the colour aesthetic? What are the disadvantages? How might the balance change if you had a larger dataset?


### Question 5

Read `?facet_wrap`. What does `nrow` do? What does `ncol` do? What other options control the layout of the individual panels? Why doesn't `facet_grid()` have `nrow` and `ncol` variables?


### Question 6

When using `facet_grid()` you should usually put the variable with more unique levels in the columns. Why?



