---
title: "01-015"
author: "Alex Cookson"
date: "15/05/2020"
output: html_document
---

```{r setup}
library(tidyverse)
```


### Question 1

What happens if you facet on a continuous variable?

-----------------------------

Let's find out by graphing `drv` vs `cyl` and facetting by `hwy`:

```{r q1-answer}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = drv, y = cyl)) +
  facet_wrap(~ hwy)
```

**ggplot** converts the continuous variable into a categorical variable for the purposes of facetting, resulting in one facet per unique value in `hwy`.



### Question 2

What do the empty cells in a plot with `facet_grid(drv ~ cyl)` mean? How do they relate to this plot?

```{r q2, eval = FALSE}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = drv, y = cyl))
```

-----------------------------

Let's start by actually graphing a plot with `facet_grid(drv ~ cyl)` to see what it looks like:

```{r q2-answer-1}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = hwy, y = cty)) +
  facet_grid(drv ~ cyl)
```

We have a facetted graph for each combination of `drv` (4, f, r) and `cyl` (4, 5, 6, 8) that has observations in at least of those. The points in the scatterplot represent the relationship between `hwy` and `cty` mileage for that combination of `drv` and `cyl` values.

If there are no points, we can assume that there are no data points for that combination of `drv` and `cyl`. For example, there are no **5**-cylinder cars with **4**-wheel or **r**ear-wheel drive.

```{r q2-answer-2}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = drv, y = cyl))
```


### Question 3

What plots does the following code make? What does `.` do?

```{r q3}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)

ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```


### Question 4

Take the first faceted plot in this section:

```{r q4, eval = FALSE}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_wrap(~ class, nrow = 2)
```

What are the advantages to using faceting instead of the colour aesthetic? What are the disadvantages? How might the balance change if you had a larger dataset?


### Question 5

Read `?facet_wrap`. What does `nrow` do? What does `ncol` do? What other options control the layout of the individual panels? Why doesn't `facet_grid()` have `nrow` and `ncol` variables?


### Question 6

When using `facet_grid()` you should usually put the variable with more unique levels in the columns. Why?



