---
title: "17-321"
author: "Alex Cookson"
date: "18/05/2020"
output: html_document
---

### Question 1

Imagine you have a directory full of CSV files that you want to read in. You have their paths in a vector, `files <- dir("data/", pattern = "\\.csv$", full.names = TRUE)`, and now want to read each one with `read_csv()`. Write the for loops that will load them into a single data frame.


### Question 2

What happens if you use `for (nm in names(x))` and `x` has no names? What if only some of the elements are named? What if the names are not unique?


### Question 3

Write a function that prints the mean of each numeric column in a data frame, along with its name. For example, `show_mean(iris)` would print:

```{r q3, eval = FALSE}
show_mean(iris)
#> Sepal.Length: 5.84
#> Sepal.Width:  3.06
#> Sepal.Length: 3.76
#> Sepal.Width:  1.20
```

(Extra challenge: what function did I use to make sure that the numbers lined up nicely, even though the variable names had different lengths?)


### Question 4

What does this code do? How does it work?

```{r q4, eval = FALSE}
trans <- list(
  disp = function(x) x * 0.0163871,
  am = function(x) {
    factor(x, labels = c("auto", "manual"))
  }
)
for (var in names(trans)) {
  mtcars[[var]] <- trans[[var]](mtcars[[var]])
}
```
