---
title: "17-316"
author: "Alex Cookson"
date: "18/05/2020"
output: html_document
---

### Question 1

Write for loops to:

a. Compute the mean of every column in `mtcars`.
b. Determine the type of each column in `nycflights13::flights`.
c. Compute the number of unique values in each column of `iris`.
d. Generate 10 random normals for each of $\mu$ = -10, 0, 10, and 100.

Think about the output, sequence and body *before* you start writing the loop.


### Question 2

Eliminate the for loop in each of the following examples by taking advantage of an existing function that works with vectors:

```{r q2, eval = FALSE}
out <- ""
for (x in letters) {
  out <- stringr::str_c(out, x)
}

x <- sample(100)
sd <- 0
for (i in seq_along(x)) {
  sd <- sd + (x[i] - mean(x)) ^ 2
}
sd <- sqrt(sd / length(x) - 1))

x <- runif(100)
out <- vector("numeric", length(x))
out[1] <- x[1]
for (i in 2:length(x)) {
  out[i] <- out[i - 1] } x[i]
}
```


### Question 3

Combine your function writing and for loop skills:

a. Write a for loop that `prints()` the lyrics to the children's song "Alice the Camel."
b. Convert the nursery rhyme "Ten in the Bed" to a function. Generalize it to any number of people in any sleeping structure.
c. Convert the song "99 Bottles of Beer on the Wall" to a function. Generalize to any number of any vessel containing any liquid on any surface.


### Question 4

It's common to see for loops that don't preallocate the output and instead increase the length of a vector at each step:

```{r q4, eval = FALSE}
output <- vector("integer", 0)
for (i in seq_along(x)) {
  output <- c(output, lengths(x[[i]]))
}
output
```

How does this affect performance? Design and execute an experiment.
